Home Nighttime Cough Monitoring

### 2025-01-14 Lilah Melzer/cough_monitor_analysis.qmd
ZINB model formatting

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(tidyverse)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
```

@@

summary(zinb)
```

@@

```{r}
zinb_sick <- update(zinb,
  fixed = Coughs ~ Night + Diagnosis + Sick,
  zi_fixed = ~ Night + Diagnosis + Sick
)
summary(zinb_sick)
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(tidyverse)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(gt)
```

@@

s <- summary(zinb)

s$coef_table_zi %>%
  data.frame() %>%
  rownames_to_column() %>%
  gt(caption = "Zero-part coefficients") %>%
  fmt_number(decimals = 3)

s$coef_table %>%
  data.frame() %>%
  rownames_to_column() %>%
  gt(caption = "Count coefficients") %>%
  fmt_number(decimals = 3)
```

For now, the results above are still on the log scale, so a negative value in the estimate column indicates a lower odds ratio or incidence rate ratio. The zero-part coefficients indicate that the odds of having a night with 0 coughs were significantly lower in the CF group (log(OR) = `r round(s$coef_table_zi["DiagnosisCF",1],3)`, OR = `r round(exp(s$coef_table_zi["DiagnosisCF",1]),3)`, p = `r format.pval(s$coef_table_zi["DiagnosisCF",4],eps = 0.001,digits = 3)`). In other words, people with CF were more likely to cough than those without CF. However, the count coefficients table indicates that given a night with more than 0 coughs, people with CF coughed at a higher rate than those without CF, but this difference was not statistically significant (log(OR) = `r round(s$coef_table["DiagnosisCF",1],3)`, OR = `r round(exp(s$coef_table["DiagnosisCF",1]),3)`, p = `r format.pval(s$coef_table["DiagnosisCF",4],eps = 0.001,digits = 3)`).

@@

```{r}
zinb_sick <- update(zinb,
  fixed = Coughs ~ Night + Diagnosis + Sick,
  zi_fixed = ~ Night + Diagnosis + Sick
)

s <- summary(zinb_sick)

s$coef_table_zi %>%
  data.frame() %>%
  rownames_to_column() %>%
  gt(caption = "Zero-part coefficients") %>%
  fmt_number(decimals = 3)

s$coef_table %>%
  data.frame() %>%
  rownames_to_column() %>%
  gt(caption = "Count coefficients") %>%
  fmt_number(decimals = 3)
```

The interpretation of these results is generally the same as above. The zero-part coefficients indicate that people with CF are still more likely to cough than people without CF (log(OR) = `r round(s$coef_table_zi["DiagnosisCF",1],3)`, OR = `r round(exp(s$coef_table_zi["DiagnosisCF",1]),3)`, p = `r format.pval(s$coef_table_zi["DiagnosisCF",4],eps = 0.001,digits = 3)`), even after adjusting for sickness. Sickness increased the odds of coughing, but the difference was not significant (log(OR) = `r round(s$coef_table_zi["SickYes",1],3)`, OR = `r round(exp(s$coef_table_zi["SickYes",1]),3)`, p = `r format.pval(s$coef_table_zi["SickYes",4],eps = 0.001,digits = 3)`). However, given a night with coughs, sickness increased the rate of cough significantly (log(OR) =  `r round(s$coef_table["SickYes",1],3)`, OR = `r round(exp(s$coef_table["SickYes",1]),3)`, p = `r format.pval(s$coef_table["SickYes",4],eps = 0.001,digits = 3)`).
